\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-03-23 ase20/compiler.tex
[ASE] Removed FaultLocalizer part

\subsection{Fault Localizer}\label{sec:localizer}
\begin{algorithm}[t]
  \caption{Fault Localization}\label{alg:fault}
  \begin{algorithmic}[1]
    \Function{FaultLocalize}{$T,n$}\Comment{$T$: failed step, $n$: size}
    \State $S = \varnothing$
    \For{$i = 0$ to $n - 1$}
    \For{$j = i$ to $n - 1$}
    \State $T'$ = a copy of $T$
    \State Substitute $T'[i..j]$ with $\tstar$
    \If{Parse($T'$) contains $\code{Dummy(}x \code{)}$ for some $x$}
    \State Insert $(x, i, j)$ into $S$
    \EndIf
    \EndFor
    \EndFor
    \While{$s = (x, i, j) \in S$}
    \If{$\exists (y, p, q) \in S$ s.t. $i \leq p \wedge q \leq j$}
    \State Remove $s$ from $S$
    \EndIf
    \EndWhile
    \State \Return $S$
    \EndFunction
  \end{algorithmic}
\end{algorithm}

To diagnose root causes of parsing failures, we support a \textsf{Fault Localizer},
which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
The basic idea is to check whether we can parse the failed algorithm step
with the assumption that a specific sub-sequence of the
failed step is successfully parsed.  We define a \textit{rule suggestion}
as such a sub-sequence of failed steps with the name of an existing compile rule.
\textsf{Fault Localizer} refines candidates of rule suggestions into the
most specific ones. It helped us when we update existing
compile rules for new versions of the specification.

The fault localization algorithm is shown in Algorithm~\ref{alg:fault}.
For a given failed step $T$ and the size of a failed input $n$, it
attempts to find a set of the most specific rule suggestions.  It
substitutes a specific sub-sequence \( T[i..j] \) of \( T \) with the
special token \( \tstar \), which represents some sub-sequence of a
failed step.  It collects a set of possible rule suggestions, and then
removes more general ones than existing suggestions.  To support this
process, we added a parsing rule  \( \code{starT} \) to each compile
rule as follows:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ||| starT ^^ { case x => Dummy("Stmt") }
// expressions
val Expr = ... ||| starT ^^ { case x => Dummy("Expr") }
\end{lstlisting}
where \( \code{starT} \) is a special basic token parser that just
checks whether a given token is the special token \( \tstar \). 
Its corresponding conversion rule is a function that returns a dummy
\( \ires \) component \( \code{Dummy} \) with a string value that
represents the name of its compile rule.

For example, let us assume that the \( \code{Expr} \) compile rule
does not have the alternative for lists:
\begin{lstlisting}[style=myScalastyle]
  "<<" ~ repsep(varT, ",") ~ ">>" ^^
       { case _ ~ x ~ _ => EList(e) } // lists
\end{lstlisting}
Then, the step 2-e-i of \textbf{ToPrimitive} becomes a failed step.
When we use the fault localization algorithm with the failed step and
its size 15, it first finds one rule suggestion for statements and four
rule suggestions for expressions as follows:
\[
\footnotesize
\! \! \! \!
  \begin{array}{c}
    (\scode{"Stmt"}, 0, 14), \;
    (\scode{"Expr"}, 3, 13), \;
    (\scode{"Expr"}, 4, 13), \;
    (\scode{"Expr"}, 6, 12), \;
    (\scode{"Expr"}, 10, 12)
  \end{array}
\]
In the \textbf{\small while} loop on lines 9--11, because the last one
is the most specific sub-sequence, it removes the other four
rule suggestions. Finally, \textsf{Fault Localizer} suggests to define
another expression compile rule for the token list \hint{}.

>>>>

% XXX removed
% \subsection{Fault Localizer}\label{sec:localizer}
% \begin{algorithm}[t]
%   \caption{Fault Localization}\label{alg:fault}
%   \begin{algorithmic}[1]
%     \Function{FaultLocalize}{$T,n$}\Comment{$T$: failed step, $n$: size}
%     \State $S = \varnothing$
%     \For{$i = 0$ to $n - 1$}
%     \For{$j = i$ to $n - 1$}
%     \State $T'$ = a copy of $T$
%     \State Substitute $T'[i..j]$ with $\tstar$
%     \If{Parse($T'$) contains $\code{Dummy(}x \code{)}$ for some $x$}
%     \State Insert $(x, i, j)$ into $S$
%     \EndIf
%     \EndFor
%     \EndFor
%     \While{$s = (x, i, j) \in S$}
%     \If{$\exists (y, p, q) \in S$ s.t. $i \leq p \wedge q \leq j$}
%     \State Remove $s$ from $S$
%     \EndIf
%     \EndWhile
%     \State \Return $S$
%     \EndFunction
%   \end{algorithmic}
% \end{algorithm}
% 
% To diagnose root causes of parsing failures, we support a \textsf{Fault Localizer},
% which takes not-yet-convertible steps dubbed ``failed steps'' as arguments.
% The basic idea is to check whether we can parse the failed algorithm step
% with the assumption that a specific sub-sequence of the
% failed step is successfully parsed.  We define a \textit{rule suggestion}
% as such a sub-sequence of failed steps with the name of an existing compile rule.
% \textsf{Fault Localizer} refines candidates of rule suggestions into the
% most specific ones. It helped us when we update existing
% compile rules for new versions of the specification.
% 
% The fault localization algorithm is shown in Algorithm~\ref{alg:fault}.
% For a given failed step $T$ and the size of a failed input $n$, it
% attempts to find a set of the most specific rule suggestions.  It
% substitutes a specific sub-sequence \( T[i..j] \) of \( T \) with the
% special token \( \tstar \), which represents some sub-sequence of a
% failed step.  It collects a set of possible rule suggestions, and then
% removes more general ones than existing suggestions.  To support this
% process, we added a parsing rule  \( \code{starT} \) to each compile
% rule as follows:
% \begin{lstlisting}[style=myScalastyle]
% // statements
% val Stmt = ... ||| starT ^^ { case x => Dummy("Stmt") }
% // expressions
% val Expr = ... ||| starT ^^ { case x => Dummy("Expr") }
% \end{lstlisting}
% where \( \code{starT} \) is a special basic token parser that just
% checks whether a given token is the special token \( \tstar \). 
% Its corresponding conversion rule is a function that returns a dummy
% \( \ires \) component \( \code{Dummy} \) with a string value that
% represents the name of its compile rule.
% 
% For example, let us assume that the \( \code{Expr} \) compile rule
% does not have the alternative for lists:
% \begin{lstlisting}[style=myScalastyle]
%   "<<" ~ repsep(varT, ",") ~ ">>" ^^
%        { case _ ~ x ~ _ => EList(e) } // lists
% \end{lstlisting}
% Then, the step 2-e-i of \textbf{ToPrimitive} becomes a failed step.
% When we use the fault localization algorithm with the failed step and
% its size 15, it first finds one rule suggestion for statements and four
% rule suggestions for expressions as follows:
% \[
% \footnotesize
% \! \! \! \!
%   \begin{array}{c}
%     (\scode{"Stmt"}, 0, 14), \;
%     (\scode{"Expr"}, 3, 13), \;
%     (\scode{"Expr"}, 4, 13), \;
%     (\scode{"Expr"}, 6, 12), \;
%     (\scode{"Expr"}, 10, 12)
%   \end{array}
% \]
% In the \textbf{\small while} loop on lines 9--11, because the last one
% is the most specific sub-sequence, it removes the other four
% rule suggestions. Finally, \textsf{Fault Localizer} suggests to define
% another expression compile rule for the token list \hint{}.
